### 2021-05-04 docs/manuscript/PLOS-MSc-Thesis.tex
Improve Fig6 caption
- A) Change "number" for "the ratio" to explain better how robutsness
was calculated.
- B) Add main results related to this graph.

\begin{figure}[!h]
 \includegraphics[width=\textwidth]{figures/results/Fig6}
 \caption{\bf Relationship between Abundance and robustness and complexity
 index.} (A) Abundance vs. Robustness. The robustness of each topology was
 calculated as the number of perturbations in which the fitness was greater or
 equal to 0.95 with respect to the total of perturbations performed.
 (B) Abundance vs. Complexity index. Each point in the plot represents one of
 the 714 network topologies.
 \label{fig:ab-rob}
\end{figure}

>>>>

\begin{figure}[!h]
 \includegraphics[width=\textwidth]{figures/results/Fig6}
 \caption{\bf Relationship between Abundance and robustness and complexity
 index.} (A) Abundance vs. Robustness. The robustness of each topology was
 calculated as the ratio of perturbations in which the fitness was greater or
 equal to 0.95 with respect to the total of perturbations performed.
 (B) Abundance vs. Complexity index. Each point in the plot represents one of
 the 714 network topologies. More complex topologies tend to be less abundant
 than simple topologies
 ($r_S = -0.316653$, $\text{p-value} = 2.25161\times10^{-18}$).
 \label{fig:ab-rob}
\end{figure}
